---
title: "Project"
author: "Mark Hu"
date: "2024-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import the dataset

```{r}
library(tidyverse)
library(lubridate)
```

```{r}
library(data.table)
client_data <- fread("Data/export.csv")
```

```{r}
client_data %>% head(10)
cleaned_cd <- na.omit(client_data)
```

```{r}
dim(cleaned_cd)
```

### Question 1

There are 64911906 observations in the dataset, with each observation representing each customer record.

```{r}
dim(cleaned_cd)
summary(cleaned_cd)
```

### Question 2 / 3

There are 1665688 customers.

```{r}
customer_num <- client_data %>% select(customer_id) %>% unique() %>% summarize(n = n())
account_num <- client_data %>% select(account_id) %>% unique() %>% summarize(n = n())

customer_num
account_num

account_num - customer_num
```

```{r}
head(cleaned_cd)
```

### Question 4

There are 310 accounts with more than 1 customer.

```{r}
extra_customer <- cleaned_cd %>%
  group_by(account_id) %>%
  distinct(customer_id) %>%
  summarize(num_customer = n()) %>% 
  filter(num_customer > 1)

extra_customer %>% head(10)
extra_customer %>% count()
```

There are 68351 customers with more than 1 account.

```{r}
extra_account <- cleaned_cd %>%
  group_by(customer_id) %>%
  distinct(account_id) %>%
  summarize(num_account = n()) %>% 
  filter(num_account > 1)

extra_account %>% head(10)
extra_account %>% count()
```

### Question 5

```{r}
time_period <- cleaned_cd %>% select(event_timestamp)
time_period %>% head(10)
```

```{r}
date <- format(time_period, "%Y-%m-%d") %>% unique()

min(date)
max(date)
```

```{r}
time <- format(time_period, "%H:%M:%S")
```

```{r}
time_info <- time %>% table()
which.max(time_info)
```

### Question 6

It is how many transactions have been made within each account

```{r}
cleaned_cd %>% filter(account_id == 1773350293)
```

```{r}
journey_data <- cleaned_cd %>% 
  group_by(account_id) %>% 
  summarize(max_journey = max(journey_steps_until_end))

#hist(journey_data)
```

### Question 7

We cleaned the original dataset, and find there is no missing value.