---
title: "Project"
author: "Mark Hu; VILLANUEVA, LUKE ADRIAN; BAKER, JESSICA; MIYAJI, TSUKASA"
date: "2024-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Import the dataset

```{r, echo=FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
```

```{r, echo=FALSE}
library(data.table)
client_data <- fread("Data/export.csv")
```

```{r, echo=FALSE, warning=FALSE}
description_data <- read_csv("Data/Event Definitions.csv", show_col_types = FALSE)
```

### Data Wrangling Process

checking that there are no NA values

```{r, echo=FALSE}
#client_data %>% head(10)
cleaned_cd <- na.omit(client_data)
```

separate `event_timestamp` variable

```{r, echo=FALSE}
# extract event_timestamp
time_period <- cleaned_cd %>% 
  select(event_timestamp)
#time_period %>% head(10)
```

```{r, echo=FALSE}
cleaned_cd <- cleaned_cd %>% 
  mutate(date = format(event_timestamp, "%Y-%m-%d")) %>% 
  mutate(time = format(event_timestamp, "%H:%M:%S"))
  
#cleaned_cd %>% head(10)
```

Regulating the event_name part for further usage

Finding that there are difference because of (), and extra variables 

```{r, echo=FALSE}
cd_event_name <- cleaned_cd %>% 
  select(event_name) %>% 
  unique() %>% 
  arrange(event_name) %>% 
  pull()
#cd_event_name
```

```{r, echo=FALSE}
useful_description <- description_data %>% 
  select(event_name, event_definition_id, stage)
useful_event_name <- useful_description %>% 
  select(event_name) %>% 
  arrange(event_name) %>% pull()
#useful_event_name
```

```{r, echo=FALSE}
cleaned_cd <- cleaned_cd %>% 
  mutate(event_name = str_replace_all(event_name, "\\(|\\)", "")) %>% 
  mutate(event_name = str_replace_all(event_name, "-", "_"))

cd_event_name <- cleaned_cd %>% 
  select(event_name) %>% 
  unique() %>% 
  arrange(event_name) %>% 
  pull()
#cd_event_name
```

still only 26 of them appears in the dataset

```{r, echo=FALSE}
inter_event_name <- intersect(cd_event_name, useful_event_name)
#inter_event_name
```

two in the data

```{r, echo=FALSE}
setdiff(cd_event_name, inter_event_name)
```

two in the description, which needs more explanantion

```{r, echo=FALSE}
setdiff(useful_event_name, inter_event_name)
```

Since there are still differences in the variable names, we decide to adhere to the description page, and delete some part fron the original data.

```{r, echo=FALSE}
modified_cd <- cleaned_cd %>% 
  inner_join(useful_description, by = c(join_by(ed_id == event_definition_id, event_name)))

#modified_cd %>% head(10)

#modified_cd %>% 
#  select(event_name) %>% 
#  unique() %>% 
#  arrange(event_name)

dim(modified_cd)
```

In conclusion, we cleaned the original dataset, and find there is no missing value. What's more, we merge two tables to add more information regarding the `ed_id` column.

### Question 1

There are 64911906 observations originally in the dataset, with each observation representing each customer purchasing record, whether approved or under view.

After cleansing, there are 56386082 of them

```{r, echo=FALSE}
dim(modified_cd)
#summary(modified_cd)
```

### Question 2 / 3

There are 1665688 customers originally, after modification there are 1665623 of them,

For users with more than one-day of record, can be defined as a returning one.

```{r, echo=FALSE}
customer_num <- modified_cd %>% select(customer_id) %>% unique() %>% summarize(n = n())
#account_num <- modified_cd %>% select(account_id) %>% unique() %>% summarize(n = n())

customer_num
#account_num
```

Thus, there are about 1362015	of them.

```{r, echo=FALSE}
returning <- modified_cd %>% 
  group_by(customer_id) %>% 
  distinct(date) %>%
  summarize(date_count = n()) %>% 
  filter(date_count > 1)

returning %>% count()
```

### Question 4

After modification, there are 310 accounts with more than 1 customer.

```{r, echo=FALSE}
extra_customer <- modified_cd %>%
  group_by(account_id) %>%
  distinct(customer_id) %>%
  summarize(num_customer = n()) %>% 
  filter(num_customer > 1)

#extra_customer %>% head(10)
extra_customer %>% count()
```

After modification, there are 68343 (befor 68351) customers with more than 1 account.

```{r, echo=FALSE}
extra_account <- modified_cd %>%
  group_by(customer_id) %>%
  distinct(account_id) %>%
  summarize(num_account = n()) %>% 
  filter(num_account > 1)

#extra_account %>% head(10)
extra_account %>% count()
```

### Question 5

showing the max and min date, or time period, would make a change if modified.

```{r, echo=FALSE}
date_info <- cleaned_cd %>% 
  select(date) %>% 
  unique() %>% 
  pull()

max(date_info)
min(date_info)
```

```{r, echo=FALSE}
date_info <- modified_cd %>% 
  select(date) %>% 
  unique() %>% 
  pull()

max(date_info)
min(date_info)
```

summarize the busiest time period, same whether modified or not.

```{r, echo=FALSE}
time_info <- cleaned_cd %>% 
  select(time) %>% 
  table() 
which.max(time_info)
```

```{r, echo=FALSE}
time_info <- modified_cd %>% 
  select(time) %>% 
  table() 
which.max(time_info)
```

### Question 6

It is how many transactions have been made within each account

```{r, echo=FALSE}
#modified_cd %>% filter(account_id == 1773350293)
```

```{r, echo=FALSE}
journey_data <- modified_cd %>% 
  group_by(account_id) %>% 
  summarize(max_journey = max(journey_steps_until_end))
```

The journey data seems to have two peeks, with median of 24 (there should be a histogram, but would exceed the page limit)

```{r, echo=FALSE, eval=FALSE}
pure_journey <- journey_data %>% select(max_journey) %>% pull()

summary(pure_journey)
hist(pure_journey, main = "Journey Histogram", xlab = "num_journey", ylab = "counts", 
     xlim = range(min(pure_journey), 500), breaks = "FD")
```

### Question 7

In conclusion, we cleaned the original dataset, and find there is no missing value. What's more, we merge two tables to add more information regarding the `ed_id` column.

But there is still one questin that needs to be answered: the difference between data and description

two in the data

```{r, echo=FALSE}
setdiff(cd_event_name, inter_event_name)
```

two in the description, which needs more explanantion

```{r, echo=FALSE}
setdiff(useful_event_name, inter_event_name)
```